### 2015-01-16 cv-body.tex
Update cv
Update doi on lobster paper
Update CV

integrated, age-structured stock assessment models. In press at ICES
Journal of Marine Science.

@@

forces interact at thermal range extremes on American lobster. Accepted
with minor revisions at Journal of Animal Ecology.

@@

(*\emph{Authors contributed equally, listed in reverse alphabetical
order}).

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2014]
Finnegan, S., \textbf{S.C. Anderson}, P.G. Harnik, C. Simpson, D.P.
Tittensor, J.E. Byrnes, Z.V. Finkel, D.R. Lindberg, L.H. Liow, R.
Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.
Pandolfi. Paleontological baselines for evaluating extinction risk in
the modern oceans. In revision.
\item[2014]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
review at Proceedings of the Royal Society B.
\end{description}

>>>>

integrated, age-structured stock assessment models. ICES Journal of
Marine Science. In press. \url{http://doi.org/10.1093/icesjms/fsu198}.

@@

forces interact at thermal range extremes on American lobster. Journal
of Animal Ecology. In press.
\url{http://doi.org/10.1111/1365-2656.12322}.

@@

(*Authors contributed equally, listed in reverse alphabetical order).

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Orzechowski, E.A., R. Lockwood, J.E. Byrnes, \textbf{S.C. Anderson}, S.
Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
Lotze, C.R. McClain, J.L. McGuire, A. O'Dea, J.M. Pandolfi, C. Simpson,
D.P. Tittensor. Determinants of extinction selectivity over the last 500
million years: a meta-analysis of marine bivalves and gastropods.
Submitted.
\item[2015]
Finnegan*, S., \textbf{S.C. Anderson}*, P.G. Harnik*, C. Simpson, D.P.
Tittensor, J.E. Byrnes, Z.V. Finkel, D.R. Lindberg, L.H. Liow, R.
Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.
Pandolfi. Paleontological baselines for evaluating extinction risk in
the modern oceans. In review. (*Authors contributed equally).
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}
